Responses to Reviews

### 2016-03-30 RMS/responses.tex
finished the final version of revision 1

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{{\bf RESPONSE: }}
\newcommand{\COMMENT}{{\bf COMMENT: }}

@@

The main changes in the paper are as following:
\begin{itemize}
\item
Section~IV about the formal model of the target implementation is
revised. Some technical details have been simplified and more literal
explanations are used to deliver our ideas.

@@

%\section{Answers to the Reviewers}
\section{Responses to Reviewer 1}
\subsection{General Comments}
\begin{itemize}

\item
\hide{ The paper shows a realistic implementation of a Rate-Monotonic
  Scheduling algorithm using Real-Time Maude (a modeling language
  based on rewriting logic) by taking into account the overhead of
  scheduling and some other details of the hardware platform. The
  correctness of the implementation with respect to the algorithm and
  the completeness of the model are verified by model checking, and
  validated within different realistic scenarios.}  
\COMMENT On the positive side, this paper presents a solid piece of
work. Periodic task scheduling is an important (and difficult)
problem, and the topic of the paper appears to be well suited within
the field of the industrial real-time systems. Overall the paper is
well structured, technically accurate, presents the work in a
comprehensive and reasonable way, and tackles theoretical as well as
practical aspects. There are two principal contributions of the paper:

@@

\ANSWER Thanks for the pros. We are happy that the work in the paper
interests the readers. We hope that it provides a new and formal way
to verify a real-time system, which is able to investigate important
problems (such as periodic task scheduling) in a more realistic level.

\item
\COMMENT The weak point is the lack of evidence of practicality,
efficiency and scalability. Since there are only small and simplistic
scenarios to analyze this model, it is difficult to judge the
effectiveness of the proposed implementation. The key scenarios appear
conveniently small to allow the implementation fully supports all
these examples, returning at the same time appropriate counterexamples
to guide and adjust the design. Is this true for larger examples of
"real world" applications within the field of industrial real-time
systems? How do the authors propose to handle very large scenarios?
How does it behave on typical real-time scheduling problems used in
industry? I would like to see more complex examples to convince the
reader of the practicability of the approach on the assumptions given
for the model, and would probably increase the mentioned benefits. The
paper does not give any directions to the above problems, and some
sentences pointing out the difficulties in the implementation of more
generic and realistic scenarios would be most welcome to understand
the real contribution of the paper.

\ANSWER Thanks for the suggestions. As mentioned in the paper, the
system under verification is a real-world RMS implementation, which is
used in an avionic control system. The scenarios presented in Section
V.B are also real scenarios from the online system. Our industrial
partner has very strict timing requirements. They use at most 5 tasks
for scheduling to avoid high overhead. They agree that the
verification results presented in the paper satisfy their practical
requirements.

@@

\item
\COMMENT One of my biggest problems with the theoretical part of this
work is that the paper is technically solid as far as I can tell, but
there's not much yet in the way of theorems and results about formal
properties in Maude. The complete and detailed proof of the Theorem 2
should be provided somewhere. If the proof of the main results of
schedulability and correctness of the model is straightforward (as is
suggested) it seems not necessary to present a complex formalism on
Real-Time Maude and all the theorems provided are natural consequences
of Theorem 1. I agree that even non-surprising results need to be
investigated in the proof of Theorem 2, some sentences pointing out
the difficulties in the theoretical formalization in Real-Time Maude
would be most welcome. Please, include (e.g., in an appendix or even
in a technical report) a detailed proof.

\ANSWER We are happy that the readers are interested in the detailed
technical proof, and we have now included it in the Appendix. It is
true that readers may be interested in the detailed proof of Theorem~2
to feel convinced of the completeness of our approach. However, the
proof needs a bit more theoretical background about rewriting logic
and more technical details of our model, which we have simplified in
the paper in order to ease the understanding of our approach. We would
prefer to refer the detailed proof to a non-anonymous technical
report, if possible, in the final version.

\item
\COMMENT Another important point which needs improvement is the
description of the implementation. I guess other readers might have
less difficulties with the motivations if they know Maude and the
Real-Time Maude extension, but if you aim for a more general audience,
it might not work. Many pages are spent for the description of the
formal modeling of the implementation and the section is hard to
read. I highly recommend the authors to thoroughly revise this part of
the paper to make it easy-to-read. It would be better preferable to
have a much shorter description of the principal insights for the
implementation followed by more convincing examples and benchmarks
with respect to related work to convince the reader of the
practicability of the approach. You should try to summarize this
section and to extend the original contribution. From my point of
view, there is a trade off in this paper between the contributions and
the presentation of the implementation.

\ANSWER Thank you for the invaluable suggestions. Section IV has been
revised. Some unnecessary detailed definitions presented as code are
removed, and replaced by more literal explanations. We hope that the
current presentation would make Section IV more easy-to-read, even for
an audience who did not know Real-Time Maude before. On the other
hand, Section VI (Related Work) is also improved. We compare our work
with the existing theoretical work and the existing verification work
in a more complete way.

\end{itemize}

\subsection{Detailed Comments}
\begin{itemize}
\item
\COMMENT Page 7, Related Work. More comparisons with other approaches
based on model checking would help to evaluate pros and cons of an
implementation with Real-Time Maude with respect to different
languages and tools. The authors should review the comparison with
[24] and [25] more thoroughly. You should benchmark your approach
against others.

\ANSWER Thanks for the pointing this out. The related work section is
now improved. More comparisons with the theoretical approaches and
with [24,25] are added. The differences with [24,25] in the models and
in the way of modeling are mainly discussed. On the other hand, it is
a bit difficult to compare the efficiency and scalability between
[24,25] and our approach. One reason is that we have a different
setting with [24] and [25], since the objectives are different: we aim
at verifying an RMS implementation from a real-world real-time system,
while [24] and [25] targeted the RMS algorithm itself. Another reason
is that [24] and [25] presented no discussion on the efficiency and
scalability. Furthermore, they used \verb|TMSVL| and an extension of
SPIN, respectively, as verification tools, which are not open-source,
making us unable to re-implement their work.

\item
\COMMENT Page 8, Conclusions. Where in the paper do you show that the
details of your "realistic" implementation are "sufficient" for the
behaviors of all real systems used in the current industry? This
should be briefly discussed.

\ANSWER Sorry for the confusion. The statement has been corrected. The
work presented in the paper aims at modeling and verifying a realistic
RMS implementation in an industrial avionic system. It is a piece of
real work in the industry. In this sense, ``sufficient'' means that
the details described in our model meet the requirements and
expectations from the users and the engineers. On the other hand, we
believe that our approach could be applied to other similar systems as
well.

\end{itemize}

\section{Responses to Reviewer 2}
\subsection{General Comments}
\begin{itemize}
\item
\COMMENT One of the problems with this paper is that it is not
completely self-contained.  Some knowledge about Real-Time Maude is
necessary in order to fully understand it.  I found the short
introduction about Real-Time Maude (section II.B) not enough for
understanding the formalism used in the rest of the paper (see details
below).

\ANSWER Thank you very much for pointing this out. The Sections II.B
and IV are improved to be more self-contained now. The idea is that,
Section II.B presents mainly an overview of Real-Time Maude, and then
Section IV describes the model with introducing necessary syntax
on-the-fly.

\item
\COMMENT Another concern is that the significance of the paper could
be much better if the paper addressed the problem of modelling RMS in
a more general way. Instead, the paper takes the form of a case study,
where the formal modelling of one specific RMS implementation is
presented, rather than a general method for modelling and analyzing
RMS implementations.

\ANSWER Thank you for the suggestion. Yes, we agree that we have two
choices to do the work presented in the paper: one is to develop a
general way to model RMS algorithms or implementations, and then
instantiate the general model to get a concrete one for our target
system; the other is to shape an accurate model of the target system
directly.

@@

\item
\COMMENT Also, the discussion about soundness and completeness of the
analysis (section V.C) is not fully developed and, once again, it
refers to the specific model rather than being a general result.

\ANSWER Thanks for this comment. The detailed proof of Theorem~2 is
now included in the Appendix. On the other hand, since we chose the
accurate way to achieve the model as discussed above, yes, the proof
is a specific one.

\end{itemize}

\subsection{Detailed Comments}
\begin{itemize}
\item
\COMMENT [Section II.B] In the definition of $IR$, it is not clear
what $s$ and $s'$ are. I guess they are states, but the concept of
state was not introduced.

\ANSWER Yes, they can be states. But more generally, they are
terms. This part has been modified to specify $s$ and $s'$ (in fact,
$t$ and $t'$ now) clearly.

\item 
\COMMENT [Section II.B] In the definition of a class, the authors
should specify that a class includes a collection of rules, otherwise
this fact may be missed.

\ANSWER Thanks very much for reminding. This is added now.

\item
\COMMENT [Section III] Page 2 right column, line -24: The
implementation is shown as schedule() in Figure 1 $\rightarrow$ The
pseudocode of schedule() is shown in Figure 1

\ANSWER Thanks for the careful reading. It is done now.

\item 
\COMMENT [Section IV.A] I don't understand the meaning of
\verb|[ctor]| in the definition of some operations (maybe because I
have no specific background on Maude). I could not find the
explanation of this writing in the introduction to Maude.

\ANSWER Sorry for missing the explanation of \verb|[ctor]|. It is now
added when \verb|[ctor]| is used for the first time.

\item
\COMMENT [Section IV.A] For the stack sort, the authors mention
operations push, pop and peek, but then you don't write the
definitions of these operations. Instead, they write the definitions
of bottom and \#, which are not explained in the text. This part
should be made clearer.

\ANSWER Sorry for the misleading presentation in the text. In fact,
\verb|bottom| and \verb|#| are constructors of sort \verb|Stack|. This
part is modified now. Some detailed definitions in code are removed,
and are replaced by more explanations. We hope that the current
presentation would make Section IV more easy-to-read.

\item
\COMMENT [Section IV.A] Also, the meaning of NzNat is not explained.

\ANSWER Sorry for this incompleteness. \verb|NzNat| meant non-zero
natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
unnecessary complexity for the readers.

\item
\COMMENT [Section V.C] In the statement of Theorem~1, the definition
of time-robust real-time rewrite theory is missing. Also, the meaning
of tick-stabilizing atomic propositions is not defined. This makes the
section not self-contained.

\ANSWER Sorry for the inconvenience for reading. In fact, the
definitions of time-robustness and tick-stabilization (which is now
replaced with tick-invariance) require more knowledge about rewriting
logic. We avoid introducing the accurate definitions of them. Instead,
now we give short descriptions of them before Theorem~1. More detailed
introduction can be found in the Appendix.

\item
\COMMENT [Section V.C] The proof of theorem 2 is missing. The authors
just indicate how the proof could be developed, but they do not
develop it. A possibility would be to point to a document where this
proof has been developed.

\ANSWER We are very happy that the readers are interested in the
detailed and technical proof, which is now included in the Appendix.
The detailed proof requires a bit more theoretical background about
rewriting logic and more details of our model, which we tried to
simplify in the paper in order to ease the understanding of our
approach. We would prefer to refer the detailed proof to a
non-anonymous technical report, if possible, in the final version.
\end{itemize}

\section{Responses to Reviewer 3}
\begin{itemize}
\item
\COMMENT RMS has many different realization methods, no comparison is
given to justify the strong point of real-time maude when applied to
RMS.

\ANSWER The comparison could be found in Section VI (and we have
expanded according to the reviewers' comments :-)). We would like to
clarify that we are \emph{not implementing} RMS, we are
\emph{verifying} it. We choose Real-Time Maude since it verifies the
model using model checking technique. If verification passes, no
deadline will be missed in the implementation as long as the model
assumptions are met.

@@

\item
\COMMENT Rate-monotonic scheduling is a very simple scheduling and has
been sufficiently investigated in the field of embedded system, the
authors claim the innovation of this paper as the implementation using
real-time maude, however, I cannot see any special point (or
advantage) when using this real-time maude in modelling RMS.

\ANSWER Thank you for the insightful comment. We agree that RMS has
been intensively studied because of its importance. However, most of
the results are based on the assumption that \emph{task switching does
  not take time}. That assumption is not realistic. Models with and
without the assumption have totally different behaviors. For instance,
as shown in Figure~2(b), in the RMS implementation we verified, the
switching from time $9$ to $11$ blocks the interrupt handling, hence
delaying the initiation time of $\tau_1$. To our knowledge, this kind
of phenomenon would not happen in the theoretical analysis
models. Although there is very few results that take into account the
switching overhead (as discussed in Section VI), none of them is
generic and our system under verification is not in their scope.

@@

\item
\COMMENT The assumptions given in IV is too rigid, which makes the
scheduling problem to be investigated by very simple, then what is the
difficulty?

\ANSWER Thank you for the question. When model checking technique is
used to verify a given system, the tool (model checker) explores the
whole system state space to check whether the given property
holds. All feasible combinations of execution traces are checked. As a
result, the state space explosion is the most common problem for a
model checker. That means the state space of the system/model is too
huge for the tool to explore with acceptable temporal and spatial
cost. The scale of the state space depends on the complexity of the
model of the system.

@@

\item
\COMMENT The description in section IV (A-E) is trivial, it can only
be viewed as a simple application of the rewriting logic.

\ANSWER Thanks for the careful reading. We agree that this is an
application of rewriting logic. In this paper, we do apply the
existing theories and techniques of rewriting logic to solve a real
industrial problem, which has not yet been investigated by this sort
of techniques, achieving an industrial contribution.

\item
\COMMENT The model checking part is not sufficiently discussed, the
authors only list the commands but not illustrate the mechanism behind
these commands.

\ANSWER Thank you for the suggestion. However, since the model checker
is not part of our contributions in the paper, we do not think it is
appropriate to illustrate the mechanism behind the model checking
commands, which may confuse the readers on the other hand.

\end{itemize}

>>>>

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{\medskip\noindent{\bf RESPONSE: }}
\newcommand{\COMMENT}{\medskip\noindent{\bf COMMENT: }}

@@

The main changes in the paper are as following, which we have also
highlighted in the revised manuscript:
\begin{itemize}
\item
Section~IV about the formal model of the target implementation is
revised. Some technical details have been simplified and more literal
explanations are used to deliver our ideas.

@@

\section{Responses to Reviewer 1}
\subsection{General Comments}

\hide{ The paper shows a realistic implementation of a Rate-Monotonic
  Scheduling algorithm using Real-Time Maude (a modeling language
  based on rewriting logic) by taking into account the overhead of
  scheduling and some other details of the hardware platform. The
  correctness of the implementation with respect to the algorithm and
  the completeness of the model are verified by model checking, and
  validated within different realistic scenarios.}

\COMMENT

On the positive side, this paper presents a solid piece of
work. Periodic task scheduling is an important (and difficult)
problem, and the topic of the paper appears to be well suited within
the field of the industrial real-time systems. Overall the paper is
well structured, technically accurate, presents the work in a
comprehensive and reasonable way, and tackles theoretical as well as
practical aspects. There are two principal contributions of the paper:

@@

\ANSWER

Thanks for the pros. We are happy that the work in the paper interests
the readers. We hope that it provides a new and formal way to verify a
real-time system, which is able to investigate important problems
(such as periodic task scheduling) in a more realistic level.

\COMMENT

The weak point is the lack of evidence of practicality, efficiency and
scalability. Since there are only small and simplistic scenarios to
analyze this model, it is difficult to judge the effectiveness of the
proposed implementation. The key scenarios appear conveniently small
to allow the implementation fully supports all these examples,
returning at the same time appropriate counterexamples to guide and
adjust the design. Is this true for larger examples of "real world"
applications within the field of industrial real-time systems? How do
the authors propose to handle very large scenarios?  How does it
behave on typical real-time scheduling problems used in industry? I
would like to see more complex examples to convince the reader of the
practicability of the approach on the assumptions given for the model,
and would probably increase the mentioned benefits. The paper does not
give any directions to the above problems, and some sentences pointing
out the difficulties in the implementation of more generic and
realistic scenarios would be most welcome to understand the real
contribution of the paper.

\ANSWER

Thanks for the suggestions. As mentioned in the paper, the system
under verification is a real-world RMS implementation, which is used
in an avionic control system. The scenarios presented in Section V.B
are also real scenarios from the online system. Our industrial partner
has very strict timing requirements. They use at most 5 tasks for
scheduling to avoid high overhead. They agree that the verification
results presented in the paper satisfy their practical requirements.

@@

\COMMENT

One of my biggest problems with the theoretical part of this work is
that the paper is technically solid as far as I can tell, but there's
not much yet in the way of theorems and results about formal
properties in Maude. The complete and detailed proof of the Theorem 2
should be provided somewhere. If the proof of the main results of
schedulability and correctness of the model is straightforward (as is
suggested) it seems not necessary to present a complex formalism on
Real-Time Maude and all the theorems provided are natural consequences
of Theorem 1. I agree that even non-surprising results need to be
investigated in the proof of Theorem 2, some sentences pointing out
the difficulties in the theoretical formalization in Real-Time Maude
would be most welcome. Please, include (e.g., in an appendix or even
in a technical report) a detailed proof.

\ANSWER

We are happy that the readers are interested in the detailed technical
proof, and we have now included it in the Appendix. It is true that
readers may be interested in the detailed proof of Theorem~2 to feel
convinced of the completeness of our approach. However, the proof
needs a bit more theoretical background about rewriting logic and more
technical details of our model, which we have simplified in the paper
in order to ease the understanding of our approach. We would prefer to
refer the detailed proof to a non-anonymous technical report, if
possible, in the final version.

\COMMENT

Another important point which needs improvement is the description of
the implementation. I guess other readers might have less difficulties
with the motivations if they know Maude and the Real-Time Maude
extension, but if you aim for a more general audience, it might not
work. Many pages are spent for the description of the formal modeling
of the implementation and the section is hard to read. I highly
recommend the authors to thoroughly revise this part of the paper to
make it easy-to-read. It would be better preferable to have a much
shorter description of the principal insights for the implementation
followed by more convincing examples and benchmarks with respect to
related work to convince the reader of the practicability of the
approach. You should try to summarize this section and to extend the
original contribution. From my point of view, there is a trade off in
this paper between the contributions and the presentation of the
implementation.

\ANSWER

Thank you for the invaluable suggestions. Section IV has been
revised. Some unnecessary detailed definitions presented as code are
removed, and replaced by more literal explanations. We hope that the
current presentation would make Section IV more easy-to-read, even for
an audience who did not know Real-Time Maude before. On the other
hand, Section VI (Related Work) is also improved. We compare our work
with the existing theoretical work and the existing verification work
in a more complete way.

\subsection{Detailed Comments}

\COMMENT

Page 7, Related Work. More comparisons with other approaches based on
model checking would help to evaluate pros and cons of an
implementation with Real-Time Maude with respect to different
languages and tools. The authors should review the comparison with
[24] and [25] more thoroughly. You should benchmark your approach
against others.

\ANSWER

Thanks for the pointing this out. The related work section is now
improved. More comparisons with the theoretical approaches and with
[24,25] are added. The differences with [24,25] in the models and in
the way of modeling are mainly discussed. On the other hand, it is a
bit difficult to compare the efficiency and scalability between
[24,25] and our approach. One reason is that we have a different
setting with [24] and [25], since the objectives are different: we aim
at verifying an RMS implementation from a real-world real-time system,
while [24] and [25] targeted the RMS algorithm itself. Another reason
is that [24] and [25] presented no discussion on the efficiency and
scalability. Furthermore, they used \verb|TMSVL| and an extension of
SPIN, respectively, as verification tools, which are not open-source,
making us unable to re-implement their work.

\COMMENT

Page 8, Conclusions. Where in the paper do you show that the details
of your "realistic" implementation are "sufficient" for the behaviors
of all real systems used in the current industry? This should be
briefly discussed.

\ANSWER

Sorry for the confusion. The statement has been corrected. The work
presented in the paper aims at modeling and verifying a realistic RMS
implementation in an industrial avionic system. It is a piece of real
work in the industry. In this sense, ``sufficient'' means that the
details described in our model meet the requirements and expectations
from the users and the engineers. On the other hand, we believe that
our approach could be applied to other similar systems as well.

\section{Responses to Reviewer 2}
\subsection{General Comments}

\COMMENT

One of the problems with this paper is that it is not completely
self-contained.  Some knowledge about Real-Time Maude is necessary in
order to fully understand it.  I found the short introduction about
Real-Time Maude (section II.B) not enough for understanding the
formalism used in the rest of the paper (see details below).

\ANSWER

Thank you very much for pointing this out. The Sections II.B and IV
are improved to be more self-contained now. The idea is that, Section
II.B presents mainly an overview of Real-Time Maude, and then Section
IV describes the model with introducing necessary syntax on-the-fly.

\COMMENT

Another concern is that the significance of the paper could be much
better if the paper addressed the problem of modelling RMS in a more
general way. Instead, the paper takes the form of a case study, where
the formal modelling of one specific RMS implementation is presented,
rather than a general method for modelling and analyzing RMS
implementations.

\ANSWER

Thank you for the suggestion. Yes, we agree that we have two choices
to do the work presented in the paper: one is to develop a general way
to model RMS algorithms or implementations, and then instantiate the
general model to get a concrete one for our target system; the other
is to shape an accurate model of the target system directly.

@@

\COMMENT

Also, the discussion about soundness and completeness of the analysis
(section V.C) is not fully developed and, once again, it refers to the
specific model rather than being a general result.

\ANSWER

Thanks for this comment. The detailed proof of Theorem~2 is now
included in the Appendix. On the other hand, since we chose the
accurate way to achieve the model as discussed above, yes, the proof
is a specific one.

\subsection{Detailed Comments}

\COMMENT

[Section II.B] In the definition of $IR$, it is not clear what $s$ and
$s'$ are. I guess they are states, but the concept of state was not
introduced.

\ANSWER

Yes, they can be states. But more generally, they are terms. This part
has been modified to specify $s$ and $s'$ (in fact, $t$ and $t'$ now)
clearly.

\COMMENT

[Section II.B] In the definition of a class, the authors should
specify that a class includes a collection of rules, otherwise this
fact may be missed.

\ANSWER

Thanks very much for reminding. This is added now.

\COMMENT

[Section III] Page 2 right column, line -24: The implementation is
shown as schedule() in Figure 1 $\rightarrow$ The pseudocode of
schedule() is shown in Figure 1

\ANSWER

Thanks for the careful reading. It is done now.

\COMMENT

[Section IV.A] I don't understand the meaning of \verb|[ctor]| in the
definition of some operations (maybe because I have no specific
background on Maude). I could not find the explanation of this writing
in the introduction to Maude.

\ANSWER

Sorry for missing the explanation of \verb|[ctor]|. It is now added
when \verb|[ctor]| is used for the first time.

\COMMENT

[Section IV.A] For the stack sort, the authors mention operations
push, pop and peek, but then you don't write the definitions of these
operations. Instead, they write the definitions of bottom and \#,
which are not explained in the text. This part should be made clearer.

\ANSWER

Sorry for the misleading presentation in the text. In fact,
\verb|bottom| and \verb|#| are constructors of sort \verb|Stack|. This
part is modified now. Some detailed definitions in code are removed,
and are replaced by more explanations. We hope that the current
presentation would make Section IV more easy-to-read.

\COMMENT

[Section IV.A] Also, the meaning of NzNat is not explained.

\ANSWER

Sorry for this incompleteness. \verb|NzNat| meant non-zero natural
numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
unnecessary complexity for the readers.

\COMMENT

[Section V.C] In the statement of Theorem~1, the definition of
time-robust real-time rewrite theory is missing. Also, the meaning of
tick-stabilizing atomic propositions is not defined. This makes the
section not self-contained.

\ANSWER

Sorry for the inconvenience for reading. In fact, the definitions of
time-robustness and tick-stabilization (which is now replaced with
tick-invariance) require more knowledge about rewriting logic. We
avoid introducing the accurate definitions of them. Instead, now we
give short descriptions of them before Theorem~1. More detailed
introduction can be found in the Appendix.

\COMMENT

[Section V.C] The proof of theorem 2 is missing. The authors just
indicate how the proof could be developed, but they do not develop
it. A possibility would be to point to a document where this proof has
been developed.

\ANSWER

We are very happy that the readers are interested in the detailed and
technical proof, which is now included in the Appendix.  The detailed
proof requires a bit more theoretical background about rewriting logic
and more details of our model, which we tried to simplify in the paper
in order to ease the understanding of our approach. We would prefer to
refer the detailed proof to a non-anonymous technical report, if
possible, in the final version.

\section{Responses to Reviewer 3}

\COMMENT

RMS has many different realization methods, no comparison is given to
justify the strong point of real-time maude when applied to RMS.

\ANSWER

The comparison could be found in Section VI (and we have expanded
according to the reviewers' comments :-)). We would like to clarify
that we are \emph{not implementing} RMS, we are actually
\emph{verifying} it. We choose Real-Time Maude since it verifies the
model using model checking technique. If verification passes, no
deadline will be missed in the implementation as long as the model
assumptions are met.

@@

\COMMENT

Rate-monotonic scheduling is a very simple scheduling and has been
sufficiently investigated in the field of embedded system, the authors
claim the innovation of this paper as the implementation using
real-time maude, however, I cannot see any special point (or
advantage) when using this real-time maude in modelling RMS.

\ANSWER

Thank you for the insightful comment. We agree that RMS has been
intensively studied because of its importance. However, most of the
results are based on the assumption that \emph{task switching does not
  take time}. That assumption is not realistic. Models with and
without the assumption have totally different behaviors. For instance,
as shown in Figure~2(b), in the RMS implementation we verified, the
switching from time $9$ to $11$ blocks the interrupt handling, hence
delaying the initiation time of $\tau_1$. This kind of phenomenon, to
our knowledge, would not happen in the theoretical analysis
models. Although there is very few results that take into account the
switching overhead (as discussed in Section VI), none of them is
generic and our system under verification is not in their scope.

@@

\COMMENT

The assumptions given in IV is too rigid, which makes the scheduling
problem to be investigated by very simple, then what is the
difficulty?

\ANSWER

Thank you for the question. When model checking technique is used to
verify a given system, the tool (model checker) explores the whole
system state space to check whether the given property holds. All
feasible combinations of execution traces are checked. As a result,
the state space explosion is the most common problem for a model
checker. That means the state space of the system/model is too huge
for the tool to explore with acceptable temporal and spatial cost. The
scale of the state space depends on the complexity of the model of the
system.

@@

\COMMENT

The description in section IV (A-E) is trivial, it can only be viewed
as a simple application of the rewriting logic.

\ANSWER

Thanks for the careful reading. We agree that this is an application
of rewriting logic. In this paper, we do apply the existing theories
and techniques of rewriting logic to solve a real industrial problem,
which has not yet been investigated by this sort of techniques,
achieving an industrial contribution.

\COMMENT

The model checking part is not sufficiently discussed, the authors
only list the commands but not illustrate the mechanism behind these
commands.

\ANSWER

Thank you for the suggestion. Our work does focus on how to model a
realistic industrial system and how to apply formal techniques (such
as model checking) to verify important properties of the system. The
mechanism behind the model checking commands (i.e. of a model checker)
is another issue.

The field of model checking techniques and the implementation of model
checkers have been intensively studied for decades. If the reviewer is
interested in the mechanism of the model checker provided by Real-Time
Maude, we would recommend the reference [A] to the reviewer:

\noindent
[A] S. Eker, J. Meseguer, and A. Sridharanarayanan, ``The Maude LTL
Model Checker'', {\it Electr. Notes Theor. Comput. Sci.}, vol. 71,
pp. 162-187, 2002.

\hide{
However, since the model checker is not part of our contributions in
the paper, we do not think it is appropriate to illustrate the
mechanism behind the model checking commands, which may confuse the
readers on the other hand.}
